FictionEro2 - Affective Impact of Fiction

### 2025-06-25 study1/analysis/2_emotions.qmd
minor

p1 <- pred1 |>
  mutate(Sex = fct_relevel(Sex, "Male", "Female")) |> 
  ggplot(aes(x=Relevance, y=Proportion)) +
  geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.2) +
  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.2) +
  geom_text(data=stars1, aes(y=y, label=label), hjust=0.5, size=3) +
  geom_rect(data=data.frame(Type="All trials", Proportion=0.1, Sex=as.factor("Male"), Outcome="Arousal", Relevance="Relevant"), 
            aes(xmin=0.8, xmax=1.2, ymin=0.5, ymax=0.80), color="#8BC34A", alpha=0) +
  geom_rect(data=data.frame(Type="All trials", Proportion=0.1, Sex=as.factor("Female"), Outcome="Arousal", Relevance="Relevant"), 
            aes(xmin=0.8, xmax=1.2, ymin=0.2, ymax=0.5), color="#8BC34A", alpha=0) +
  facet_grid(Outcome~Sex, switch="y") +
  scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_bw() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9, color="black"),
        legend.text = element_text(size = 10),
        legend.position = "bottom") +
  labs(color="Images presented as:",
       tag = "A")
p1
```

>>>>

p1 <- pred1 |>
  mutate(Sex = fct_relevel(Sex, "Male", "Female")) |> 
  ggplot(aes(x=Relevance, y=Proportion)) +
  geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.2) +
  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.2) +
  geom_text(data=stars1, aes(y=y, label=label), hjust=0.5, size=3) +
  geom_rect(data=data.frame(Type="All trials", Proportion=0.1, Sex=as.factor("Male"), Outcome="Arousal", Relevance="Relevant"), 
            aes(xmin=0.8, xmax=1.2, ymin=0.5, ymax=0.80), color="#8BC34A", alpha=0) +
  geom_rect(data=data.frame(Type="All trials", Proportion=0.1, Sex=as.factor("Female"), Outcome="Arousal", Relevance="Relevant"), 
            aes(xmin=0.8, xmax=1.2, ymin=0.2, ymax=0.5), color="#8BC34A", alpha=0) +
  facet_grid(Outcome~Sex, switch="y") +
  scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9, color="black"),
        legend.text = element_text(size = 10),
        legend.position = "bottom") +
  labs(color="Images presented as:",
       tag = "A")
p1
```

### 2025-06-25 study2/analysis/2_emotion.qmd
minor

```{r Arousal Believed}
m_a_b <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition|Participant) + (Condition|Stimulus),
                        data=filter(df, ConditionBelief == "True"), 
                        family=glmmTMB::ordbeta(),
                        control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m_a_b)
```

@@

```{r Enticement Believed1}
m_e_b <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + (Condition| Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r Valence Believed1}
m_v_b <- glmmTMB::glmmTMB(Valence ~ Gender /Condition + (Condition| Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m_v_b)

@@

```{r Emotionality Model}
m_em <- glmmTMB::glmmTMB(Emotionality ~ Gender /StimuliType/ Condition + (Condition| Participant) + (1|Stimulus),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m_em)

marginaleffects::avg_slopes(m_em, variables="Condition", by="Gender", re.form=NA) |>
  results_table()
```

@@

```{r}
#| fig-height: 12
#| fig-width: 7

pred1 <- rbind(
  marginaleffects::avg_predictions(m_arousal, by=c("Gender", "StimuliType", "Condition"), newdata = "mean", re.form=NA) |>
  as.data.frame() |> 
  mutate(Outcome="Arousal"),
  marginaleffects::avg_predictions(m_enticement, by=c("Gender","StimuliType",  "Condition"), newdata = "mean", re.form=NA) |>
  as.data.frame() |> 
  mutate(Outcome="Enticement"),
  marginaleffects::avg_predictions(m_valence, by=c("Gender", "StimuliType", "Condition"), newdata = "mean", re.form=NA) |>
  as.data.frame() |> 
  mutate(Outcome="Valence")
)

stars1a <- data.frame(label=c("**","***", "**", "***", "***", "***"),
                    Gender=fct_relevel(c("Male", "Female", "Male", "Female", "Male", "Female"), "Male"),
                    Outcome=c("Arousal","Arousal", "Enticement", "Enticement", "Valence", "Valence"),
                    Condition=c("Photograph", "Photograph", "Photograph", "Photograph", "Photograph", "Photograph"), 
                    x=c(1.5, 1.5, 1.5, 1.5, 1.5, 1.5), 
                    y = c(0.53, 0.40, 0.6, 0.51, 0.62, 0.58))

stars1b <- data.frame(label=c("*","**", "*","*"),
                    Gender=fct_relevel(c("Male", "Male", "Male","Female"), "Male"),
                    Outcome=c("Arousal", "Enticement", "Enticement","Valence"),
                    x=c(1, 1, 2, 2),
                    y=c(0.60, 0.65, 0.56, 0.6))

p1 <- pred1 |>
  mutate(Gender = fct_relevel(Gender, "Male", "Female")) |> 
  ggplot(aes(x=StimuliType, y=estimate)) +
  geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.4, key_glyph = "path") +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high, color=Condition), position = position_dodge(width=0.2), size=0.3) +
  geom_text(data=stars1a, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, key_glyph = "blank", size=3) +
  geom_text(data=stars1b, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
  # geom_rect(data=data.frame(Type="All trials", estimate=0.1, Gender=as.factor("Male"), Outcome="Arousal"),
  #           aes(xmin=0.8, xmax=1.2, ymin=0.35, ymax=0.6), color="#8BC34A", alpha=0) +
  # geom_rect(data=data.frame(Type="All trials", estimate=0.1, Gender=as.factor("Female"), Outcome="Arousal"),
  #           aes(xmin=0.8, xmax=1.2, ymin=0.3, ymax=0.5), color="#8BC34A", alpha=0) +
  facet_grid(Outcome~Gender, switch="y", scales ="free") +
  scale_y_continuous(limits=c(0.20, 0.8), labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_bw() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9, color="black"),
        legend.text = element_text(size = 10),
        legend.position = ) +
  labs(color="Images presented as:")

@@

```{r}
m1 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition | Participant) + (1|Stimulus),data = df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
m2 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition | Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
m3 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition  + (Condition | Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True", Feedback_AILessAttractive=="True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
m4 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition  + (Condition | Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True", Feedback_AIMoreAttractive=="True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

stars2 <- data.frame(label=c("**", "***", "*"),
                    Gender=fct_relevel(c("Male", "Male", "Male")),
                    Type=c("All trials", "Believed trials" ,"'AI was more attractive'"),
                    y=c(0.52, 0.56, 0.66))

pred2 <- rbind(
  estimate_relation(m1) |> 
    mutate(Type = "All trials"),
  estimate_relation(m2) |> 
    mutate(Type = "Believed trials"),
  estimate_relation(m3) |> 
    mutate(Type = "'AI was less attractive'"),
  estimate_relation(m4) |> 
    mutate(Type = "'AI was more attractive'"))

p2 <- pred2 |> 
  mutate(Type = fct_relevel(Type, "All trials", "Believed trials", "'AI was less attractive'", "'AI was more attractive'")) |> 
  ggplot(aes(x=Type, y=Predicted)) +
  geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.1) +
  geom_bar(stat="identity", aes(fill=Condition), position = position_dodge(width=0.2), width=0.2, alpha=0.6) +
  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.2) +
  geom_rect(data=data.frame(Type="All trials", Predicted=0.1, Gender=as.factor("Male")),
            aes(xmin=0.7, xmax=1.3, ymin=0.35, ymax=0.55), color="#8BC34A", alpha=0) +
  geom_rect(data=data.frame(Type="All trials", Predicted=0.1, Gender=as.factor("Female")),
            aes(xmin=0.7, xmax=1.3, ymin=0.30, ymax=0.48), color="#8BC34A", alpha=0) +
  geom_text(data=stars2, aes(y=y, label=label), hjust=0.5, size=3) +
  facet_grid(~Gender) +
  scale_y_continuous(labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  labs(y="Arousal",
       tag = "B") +
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9),
        axis.text.y = element_text(size = 8),
        axis.title.y = element_text(size = 10),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        legend.position = "none")

@@

1. Models for arousal, enticement, and valence had singularity issues when also adding condition as random slope for stimuli
2. 'Other' was removed due to the very small percentage of individuals identifying as such.
3. 'Porn' factor was not computed, instead sexual activity and frequency of watching porn were treated seperate. 
4. Missing final figures and interpretation of belief as influencing emotional ratings of images
5.[The calculations for the BAIt/GAAIS dimensions were based on the validation of the BAIT scale](https://realitybending.github.io/FictionEro/study1/analysis/1_cleaning.html)

>>>>

```{r Arousal Believed}
m <- glmmTMB::glmmTMB(Arousal ~ Gender / StimuliType/Condition + (Condition|Participant) + (Condition|Stimulus),
                        data=filter(df, ConditionBelief == "True"), 
                        family=glmmTMB::ordbeta(),
                        control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r Enticement Believed1}
m <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + (Condition| Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r Valence Believed1}
m <- glmmTMB::glmmTMB(Valence ~ Gender /Condition + (Condition| Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

@@

```{r Emotionality Model}
m_emotionality <- glmmTMB::glmmTMB(Emotionality ~ Gender /StimuliType/ Condition + (Condition| Participant) + (1|Stimulus),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m_emotionality)

marginaleffects::avg_slopes(m_emotionality, variables="Condition", by="Gender", re.form=NA) |>
  results_table()
```

@@

```{r}
#| fig-height: 7
#| fig-width: 7

pred1 <- rbind(
  modelbased::estimate_means(m_arousal, by=c("Gender", "StimuliType", "Condition"), backend = "emmeans") |>
  as.data.frame() |> 
  mutate(Outcome="Arousal"),
  modelbased::estimate_means(m_enticement, by=c("Gender","StimuliType",  "Condition"), backend = "emmeans") |>
  as.data.frame() |> 
  mutate(Outcome="Enticement"),
  modelbased::estimate_means(m_valence, by=c("Gender", "StimuliType", "Condition"), backend = "emmeans") |>
  as.data.frame() |> 
  mutate(Outcome="Valence")
)

# stars1a <- data.frame(label=c("**","***", "**", "***", "***", "***"),
#                     Gender=fct_relevel(c("Male", "Female", "Male", "Female", "Male", "Female"), "Male"),
#                     Outcome=c("Arousal","Arousal", "Enticement", "Enticement", "Valence", "Valence"),
#                     Condition=c("Photograph", "Photograph", "Photograph", "Photograph", "Photograph", "Photograph"), 
#                     x=c(1.5, 1.5, 1.5, 1.5, 1.5, 1.5), 
#                     y = c(0.53, 0.40, 0.6, 0.51, 0.62, 0.58))

stars1b <- data.frame(label=c("*"),
                    Gender=fct_relevel(c("Male"), "Male"),
                    Outcome=c("Arousal"),
                    x=1,
                    y=0.60)

stars1b <- data.frame(label=c("*","**", "*","*"),
                    Gender=fct_relevel(c("Male", "Male", "Male","Male"), "Male"),
                    Outcome=c("Arousal", "Enticement", "Enticement","Valence"),
                    x=c(1, 1, 2, 1),
                    y=c(0.60, 0.65, 0.56, 0.68))

p1 <- pred1 |>
  mutate(Gender = fct_relevel(Gender, "Male", "Female")) |> 
  ggplot(aes(x=StimuliType, y=Proportion)) +
  geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.4, key_glyph = "path") +
  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.3) +
  geom_text(data=stars1b, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=6) +
  geom_rect(data=data.frame(StimuliType = "Individual", Proportion=0.1, Gender=as.factor("Male"), Outcome="Arousal"),
            aes(xmin=0.8, xmax=1.2, ymin=0.35, ymax=0.7), color="#8BC34A", alpha=0, ) +
  geom_rect(data=data.frame(StimuliType = "Individual",Proportion=0.1, Gender=as.factor("Female"), Outcome="Arousal"),
            aes(xmin=0.8, xmax=1.2, ymin=0.2, ymax=0.5), color="#8BC34A", alpha=0) +
  facet_grid(Outcome~Gender, switch="y", scales ="free") +
  scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9, color="black"),
        legend.text = element_text(size = 10),
        legend.position = ) +
  labs(color="Images presented as:")

@@

```{r}
m1 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition | Participant) + (1|Stimulus),data = df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
m2 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition | Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
m3 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition  + (Condition | Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True", Feedback_NoFacesAttractive=="True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
m4 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition  + (Condition | Participant) + (1|Stimulus),
                      data=filter(df, ConditionBelief == "True", Feedback_AIMoreAttractive=="True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

stars2 <- data.frame(label=c("**", "***", "*", "*", "*"),
                    Gender=fct_relevel(c("Male", "Male", "Male", "Female", "Female")),
                    Type=c("All trials", "Believed trials" ,"'AI was more attractive'", "Believed trials", "'No faces were attractive'"),
                    y=c(0.52, 0.56, 0.66, 0.47, 0.39))

pred2 <- rbind(
  estimate_relation(m1) |> 
    mutate(Type = "All trials"),
  estimate_relation(m2) |> 
    mutate(Type = "Believed trials"),
  estimate_relation(m3) |> 
    mutate(Type = "'No faces were attractive'"),
  estimate_relation(m4) |> 
    mutate(Type = "'AI was more attractive'"))

p2 <- pred2 |> 
  mutate(Type = fct_relevel(Type, "All trials", "Believed trials", "'No faces were attractive'", "'AI was more attractive'")) |> 
  ggplot(aes(x=Type, y=Predicted)) +
  geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.1) +
  geom_bar(stat="identity", aes(fill=Condition), position = position_dodge(width=0.2), width=0.2, alpha=0.6) +
  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.2) +
  geom_rect(data=data.frame(Type="All trials", Predicted=0.1, Gender=as.factor("Male")),
            aes(xmin=0.7, xmax=1.3, ymin=0.35, ymax=0.55), color="#8BC34A", alpha=0) +
  geom_rect(data=data.frame(Type="All trials", Predicted=0.1, Gender=as.factor("Female")),
            aes(xmin=0.7, xmax=1.3, ymin=0.30, ymax=0.48), color="#8BC34A", alpha=0) +
  geom_text(data=stars2, aes(y=y, label=label), hjust=0.5, size=3) +
  facet_grid(~Gender) +
  scale_y_continuous(labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  labs(y="Arousal",
       tag = "B") +
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9),
        axis.text.y = element_text(size = 8),
        axis.title.y = element_text(size = 10),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        legend.position = "none")

@@

1. Models for arousal, enticement, and valence had singularity issues when also adding condition as random slope for stimuli
2. 'Other' was removed due to the very small percentage of individuals identifying as such.
3. 'Porn' factor was not computed, instead sexual activity and frequency of watching porn were treated seperate. 
4. Missing final figures and interpretation of belief as influencing emotional ratings of images
5. [The calculations for the BAIt/GAAIS dimensions were based on the validation of the BAIT scale](https://realitybending.github.io/FictionEro/study1/analysis/1_cleaning.html)
